% \begin{biography}
    \profile{Hiroki Kuzuno}{%
    %\bio{}
    %{\bf Hiroki Kuzuno}
      %
      %received the Ph.D. degree in engineering from Okayama University, Japan, in 2020.
      received an M.E.\ degree in Information Science from Nara
      Institute of Science and Technology, Japan, in 2007, and a
      Ph.D.\ in Computer Science from Okayama University, Japan in 2020.
      %
      %Since joining SECOM in 2007, 
      Currently, he is an Assistant Professor at Kobe University, Japan.
      %In 2021, he became an Assistant Professor with the Graduate
      %School of Natural Science and Technology at Kobe University.
      %
      His research focuses on computer security specifically on operating systems and networks.
    %
    %He is now a Cyber-Security Researcher at SECOM Singapore and INTERPOL Global Complex for Innovation.
    %
    He is a member of IEICE and IPSJ.}
    %\endbio
    
    \profile{Toshihiro Yamauchi}{%
    %\bio{}
    %{\bf Toshihiro Yamauchi}
      %
      received B.E.\, M.E.\, and Ph.D.\ degrees in Computer Science from Kyushu University,
      Japan in 1998, 2000, and 2002, respectively.
      %
      In 2001, he was a Research Fellow of the Japan Society for the
      Promotion of Science. In 2002, he became a Research Associate with
      the Faculty of Information Science and Electrical Engineering at Kyushu
      University. In 2005, he became an Associate Professor with the Graduate
      School of Natural Science and Technology at Okayama University, Japan.
      %
      He has been serving as a Professor with Okayama University since
      2021. His research interests include operating systems and computer
      security. He is a member of IPSJ, IEICE, ACM, USENIX and IEEE\@.}
    
    %
% \end{biography}
    %\endbio
    